### 2023-11-27 main.tex
''
iuyfg

\begingroup
% \centering
\begin{center}
 \begingroup\LARGE
%\bf Multispecies stirring process: duality and exact solution
\bf Exact solution of the multispecies stirring process \\
 with open boundaries
\par\endgroup
 \vspace{3.5em}
 \begingroup\large \bf
% {Rouven Frassek}
 \par\endgroup
\vspace{2em}

\begingroup\sffamily 
%  
% Università degli Studi di Modena e Reggio Emilia
%University of Modena and Reggio Emilia, 
%\\Department of Physics, Informatics and Mathematics,\\
%Via G. Campi 213/b, 41125 Modena, Italy\\ 
\par\endgroup
\vspace{2em}

@@

\tableofcontents

@@

	\item \textit{Correlations} (Section \ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find when $\nu>1$, however correlation can be formally written. 	
	\item \textit{Instantaneous thermalization} (Section \ref{Subsection-Thermalized}): starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Also for this thermalized process we prove duality. 	
	\item \textit{Reaction-diffusion process}(Section \ref{Subsection-RD}): a further dynamics is added. Particle can now change type. The model is carefully constructed with the goal of having the average densities evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Duality for the boundary driven process is also proved.

@@

In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). All the processes considered, denoted by $\left(\bm{n}(t)\right)_{t\geq0}$ with the generator specified in each subsection, will be defined on the space

@@

	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega_{x}
 The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case. The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively. To recall it we denote this dual space by $\widetilde{\Omega}_{L}$, i.e.

@@

	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\alpha_{a}}{|\alpha|}

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given from \eqref{siteDualGenerator} absorbing particles from sites $\{1\}$ and $\{L\}$ and putting them at extra-sites $\{0\}$ and $\{L+1\}$ respectively. The duality function reads is \eqref{dualityElements} specified on the chain. 

@@

The dual process has absorbing boundaries. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process.\\
We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$. For every $m\in\{1,\ldots,L\}$ we consider  $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$. We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\
		\xi_{a}^{x}=0\qquad &\text{otherwise}
The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{C(\nu,m)}\dt
where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal occupancy $\nu$. 
Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$points correlations at non-equilibrium steady state. The following equalities hold using ergodicity and duality:
		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\mathcal{Y}_{a_{k}}^{x_{k}}=n_{a_{k}}^{x_{k}}\}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{t_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})
here we recall that, generalizing Corollary \ref{Corolollary-ABS_Corr-abstract}, %that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and 
	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
 These correlations can be computed once the absorption probabilities are known. For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. However, these absorption probabilities for higher point correlations fulfil some difference equations that are not easy to solve.

@@

In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality,KMP}). The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles. The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\epsilon=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\epsilon$. 

@@

Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ such that $\forall a\in\{1,\ldots,N\}$  $r_{a}\in \{0,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints 

@@

The proof of proposition \ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.

@@

where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$. These average occupations evolves according to the evolution equation

@@

This equation is endowed with boundary conditions $\rho_{a}^{\text{left}},\rho_{\overline{a}}^{\text{left}}$ on the left and $\rho_{a}^{\text{right}},\rho_{\overline{a}}^{\text{right}}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}). For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}). In view of what have been proved in the previous sections of this work, some questions arise naturally:

@@

 We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{0}$ and $\rho_{a}^{L+1}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{0}=\nu$.

@@

\subsubsection{The process on a chain}

@@

with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator

@@

Observe that $h_{c}(\cdot)$ is surjective and injective, and thus invertible. \\

@@

for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\nu$. \\

@@

\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}. 

@@

where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$. \\For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 

@@

On the occupation variable $n_{a}^{L}$ the action is similar. Therefore, using the evolution equation \eqref{EE-density} for the average densities and  the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain the desired system of $N-1$ difference-differential equations \eqref{NSpeciesRD}. For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question we addressed to at the beginning of this section. 

@@

	Indeed, we impose the detailed balance for the stirring-mutation generator $\mathcal{L}_{x,x+1}^{c}$, for arbitrary $c\in \{1,\ldots,N-2\}$. Consider the transition 
			\bm{n} \to\bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c(a)}}^{x+1}-\delta_{b}^{x+1}
		we obtain that 
			p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
		that is verified if $p_{a}=p_{b}$ for all $a,b\in \{1,\ldots,N-1\}$. A similar argument for the generator $\mathcal{L}^{m}$ gives the same conditions for the $p$'s. Considering the boundary generators, one obtain the result.}

@@

	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{h_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{h_{c}(\ell)N}^{x+1}\right)\right\}
	\\=&0\dt

@@

In the last equality we used the fact that map $h_{c}(\cdot)$ is surjective. \\

@@

Already for two-point correlations the computations become more involving and hard to solve.

@@

	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
Where we used {\color{blue}

@@

and }the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.

>>>>

\begingroup
% \centering
\begin{center}
 \begingroup\LARGE
\bf Exact solution of the multi-species stirring process \\
 with open boundaries
\par\endgroup
 \vspace{3.5em}
 \begingroup\large \bf
 {Francesco Casini$^{(a,b)}$, Rouven Frassek$^{(b)}$, Cristian Giardin\`a$^{(b)}$}
 \par\endgroup
\vspace{2em}

\begingroup\sffamily

 %Università degli Studi di Modena e Reggio Emilia
(a) University of Parma, \\
Department of ....,\\
Via ...., .... Parma, Italy\\

 \vspace{.5cm}

(b) University of Modena and Reggio Emilia, \\
Department of Physics, Informatics and Mathematics,\\
Via G. Campi 213/b, 41125 Modena, Italy\\ 
\par\endgroup
\vspace{2em}

@@

\newpage
\tableofcontents

@@

	\item \textit{Correlations} (Section \ref{Subsection-ss-nonI}): exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find when $\nu>1$. We give 
	in Appendix \ref{appendix-1pts-general} the expression for the one-point correlation.
	\item \textit{Instantaneous thermalization} (Section \ref{Subsection-Thermalized}): starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistributed on each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Also for this thermalized process we prove duality. 	
	\item \textit{Reaction-diffusion process} (Section \ref{Subsection-RD}): a further dynamics is added. Particle can now change type. The model is carefully constructed with the goal of having the average densities evolving as a closed system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Duality for the boundary driven process is also proved.

@@

In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can host $\nu\geq 1$ particles, whose type is chosen among the $N$ available ones. The graph of the dual process is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). The processes considered in this section will be denoted with same name $\left(\bm{n}(t)\right)_{t\geq0}$, their generator will be specified in each subsection. 
We use the notation of Section \ref{sectionDuality} specialized to the one dimensional chain with $\nu >1$.
E.g. the state space is denoted by 

@@

	\Omega_{L}=\bigotimes_{x=1}^{L} \Omega_{x}\,.
 The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case. The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively. 
 We denote the space of the dual process by $\widetilde{\Omega}_{L}$, i.e.

@@

	\rho_{a}^{\text{left}}=\frac{\alpha_{a}}{|\alpha|},\qquad \qquad \rho_{a}^{\text{right}}=\frac{\beta_{a}}{|\beta|}\,.

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $\{1\}$ and $\{L\}$ and put them at extra-sites $\{0\}$ and $\{L+1\}$ respectively. The duality function reads is \eqref{dualityElements} specified on the chain. 

@@

%The dual process has absorbing boundaries. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process.\\
We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$. For every $m\in\{1,\ldots,L\}$ we consider  $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$. We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\
		\xi_{a}^{x}=0\qquad &\text{otherwise}
	\end{cases}\dt
\end{equation}
The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that
\begin{equation}
	D(\bm{n},\bm{\xi})= \frac{\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}}{C(\nu,m)}\dt
\end{equation}
where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal occupancy $\nu$. 
Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$points correlations at non-equilibrium steady state. The following equalities hold using ergodicity and duality:
\begin{equation}\label{ExptationSS}
	\begin{split}
		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\mathcal{Y}_{a_{k}}^{x_{k}}=n_{a_{k}}^{x_{k}}\}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\\&=
		\sum_{t_{1}=0}^{|\xi_{1}|}\ldots\sum_{t_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{t_{a}}\left(\rho_{a}^{\text{right}}\right)^{|\xi_{a}|-t_{a}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})
	\end{split}
\end{equation}
here we recall that, generalizing Corollary \ref{Corolollary-ABS_Corr-abstract}, %that $\rho_{\alpha}^{L}=\frac{\alpha_{a}}{|\alpha|}$, $\rho_{\alpha}^{R}=\frac{\beta_{a}}{|\beta|}$ are the boundary densities and 
\begin{equation}\label{Pass} 
	\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{N})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(t_{a}\delta_{a}^{0}+(|\xi_{a}|-t_{a})\delta_{a}^{L+1}\right)| \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
 These correlations can be computed once the absorption probabilities are known. For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. The absorption probabilities for higher point correlations fulfill  difference equations.

@@

In this subsection we aim to extend to the multi-species stirring process the concept of \textit{instantaneous thermalization limit} (see \cite{carinci2013duality,KMP}). The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles. The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} as follows: for each bond $(x,x+1)$ the total number of particles $\epsilon=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\epsilon$. 

@@

Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ are such that $\forall a\in\{1,\ldots,N\}$ we have $r_{a}\in \{0,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints 

@@

The proof of Proposition \ref{proposition-dualityTHM} is standard. For the sake of completeness we report it in Appendix \ref{appendix-dualityThermalized}.

@@

where $\mathbb{E}_{\mu_{0}}$ denotes the expectation with respect to the law of the Markov process $(\bm{n}(t))_{t\geq 0}$ initialized with arbitrary initial measure $\mu_{0}$. Calling
$\mathcal{L}^{rd}$ the generator of the process, these average occupations evolves according to the evolution equation

@@

This equation is endowed with boundary conditions $\rho_{a}^{\text{left}},\rho_{\overline{a}}^{\text{left}}$ on the left and $\rho_{a}^{\text{right}},\rho_{\overline{a}}^{\text{right}}$ on the right. 
The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}). For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}). In view of what have been proved in the previous sections of this work, some questions arise naturally:

@@

 We assume that the boundary conditions of the above difference differential system are given and denoted by $\rho_{a}^{\text{left}}$ and $\rho_{a}^{\text{right}}$ for all $a\in\{1,\ldots,N-1\}$ at left and right respectively, further assuming that $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\sum_{a=1}^{N}\rho_{a}^{\text{right}}=\nu$.

@@

\subsubsection{The reaction-diffusion process on a chain}

@@

where $\mathcal{L}_{x,x+1}$ is the edge-generator \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce the \textit{stirring-mutation} generator

@@

Observe that $h_{c}(\cdot)$ is surjective and injective, and thus invertible.

@@

for every $a\in\{1,\ldots,N\}$. Moreover, with this choice we have that $\sum_{a=1}^{N}\alpha_{a}=\nu(\sigma_{11}+(N-1)\sigma_{12})$ and $\sum_{a=1}^{N}\rho_{a}^{\text{left}}=\nu$. 

@@

%\begin{remark}: we stress that, up to a specific choice of the $\alpha$'s ($\beta$'s), the left (right) boundary generator $\mathcal{L}_{\text{left}}^{rd}$ ($\mathcal{L}_{\text{right}}^{rd}$) has the form of the one of the multi-species stirring process \eqref{siteGenerator}. 

@@

where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$. For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 

@@

On the occupation variable $n_{a}^{L}$ the action is similar. Therefore, using the evolution equation \eqref{EE-density} for the average densities and  the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain the desired system of $N-1$ difference-differential equations \eqref{NSpeciesRD}. For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. 
%This answers the first question we addressed to at the beginning of this section. 

@@

%	Indeed, we impose the detailed balance for the stirring-mutation generator $\mathcal{L}_{x,x+1}^{c}$, for arbitrary $c\in \{1,\ldots,N-2\}$. Consider the transition 
%			\bm{n} \to\bm{n}-\delta_{a}^{x}+\delta_{h_{c}(b)}^{x}+\delta_{h_{c(a)}}^{x+1}-\delta_{b}^{x+1}
%			\end{equation*} 
%		we obtain that 
%			p_{a}p_{b}=p_{h_{c}(a)}p_{h_{c}(b)}
%		\end{equation*}
%		that is verified if $p_{a}=p_{b}$ for all $a,b\in \{1,\ldots,N-1\}$. A similar argument for the generator $\mathcal{L}^{m}$ gives the same conditions for the $p$'s. Considering the boundary generators, one obtain the result.}

@@

	\sum_{a,b=1}^{N-1}\sum_{d,\ell=1}^{N}\left\{\left(E_{dN}^{x}-E_{h_{c}(\ell)N}^{x}\right)\otimes \left(E_{dN}^{x+1}-E_{h_{c}(\ell)N}^{x+1}\right)\right\}=0\dt

@@

In the last equality we used the fact that map $h_{c}(\cdot)$ is surjective. 

@@

%Already for two-point correlations the computations become more involving and hard to solve.

@@

	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{\text{left}}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)
Where we used 

@@

and the multinomial theorem in the last equality. \\ We now consider the second addend in the curly brackets of \eqref{ProvaBordoTH}.
